\thesistitle

### 2019-08-25 sections/clonerefactor.tex
Revamp Relation

Every clone class only has a single relation, which is the first relation from the above list that the clone class applies to. For instance: all ``Superclass'' clones also apply to ``Same Hierarchy'', but because ``Superclass'' is earlier in the list they will get the ``Superclass'' relation. This is because the items earlier in the list denote a more favorable refactoring.

To determine the relation for a given clone class, we compare each node in a clone instance with the respective nodes in each other clone instance within a clone class. So for a clone class with x clone instances and each clone instance has y nodes, we perform:

\begin{equation}\label{eq:sameclass}
\frac{x * (x + 1)}{2} * y
\end{equation}

comparisons to determine the relation. Each of these checks will result in one of the relations from the list above. Of these relations, the item lowest in the list is going to be the relation of the clone class. So for instance, if a clone class has 15 nodes that denote a \textit{Superclass} relation but 3 nodes are \textit{Unrelated}, the clone class becomes \textit{Unrelated}.

@@

Cloned nodes are flagged as \textit{Same method} if these nodes are found in the same method. We define the method as the first method declaration that is encountered when following the parent nodes in the AST for a given cloned node. Please note that a clone instance may not always be in a method, for which this predicate will fail.

Cloned nodes are flagged as \textit{Same class} if these nodes are found in the same class. We define the class as the first class declaration that is encountered when following the parent nodes in the AST for a given cloned node.

\subsubsection{Common Hierarchy}
Clones that are in a common hierarchy can be refactored by using the ``Extract Method'' refactoring method followed by ``Pull Up Method'' until the method reaches a location that is accessible by all clone instances. However, the more often ``Pull Up Method'' has to be used, the more detrimental the effect is on system design. This is because putting a lot of functionality in classes higher up in an inheritance structure can result in the ``God Object'' anti-pattern. A god object is an object that knows too much or does too much.

Cloned nodes are flagged as \textit{Superclass} if the classes in which these nodes are found are parent and child class of each other. Cloned nodes are flagged as \textit{Siblings} if the classes in which these nodes are found all share the same parent and this parent class is not external. Cloned nodes are flagged as \textit{First Cousin} if the classes in which these nodes are found all share the same grandparent and this grandparent class is not external.

Cloned nodes are flagged as \textit{Ancestor} if the classes in which these nodes are found are recursively the parent of an antecedent. Cloned nodes are flagged as \textit{Same Hierarchy} if the classes in which these nodes are found are all in the same inheritance hierarchy and not linked by any external classes.

@@

To check whether two cloned nodes have a \textit{Same Direct Interface} relation, we check that the classes to which these nodes belong both implement the same interface type. To check whether two cloned nodes have a \textit{Same Indirect Interface} relation, we recursively walk all types the class or interface of the cloned nodes implement and extend. The common interface that is closest to the cloned node in terms of depth of recursion will be flagged as the refactoring candidate.

@@

Cloned nodes are flagged \textit{No Direct Superclass} if they are in classes that do currently not have a parent. This marks the opportunity for creating a superclass abstraction and placing the extracted method there. Cloned nodes are flagged \textit{No Indirect Superclass} if any of their ancestors do not have a parent. In such a case, it would be possible to create such an abstraction for the ancestor that does not have a parent.

Cloned nodes are flagged \textit{External Superclass} if they are in a class which has an external parent. Cloned nodes are flagged \textit{External Ancestor} if one of their ancestors has an external parent. Both of these relations obstruct the possibility of creating a superclass abstraction. In such a case, an interface abstraction could be created to make their relation explicit.

>>>>

Every clone class only has a single relation, which is the first relation from the above list that the clone class applies to. For instance: all ``Superclass'' clones also apply to ``Same Hierarchy'', but because ``Superclass'' is earlier in the above list they will get the ``Superclass'' relation. This is because the items earlier in the above list denote a more favorable refactoring.

When CloneRefactor applies automated refactorings, it uses this inheritance relation to see where it must place the refactored code. We explain this for each relation category over the following sections.

%To determine the relation for a given clone class, we compare each node in a clone instance with the respective nodes in each other clone instance within a clone class. %So for a clone class with x clone instances and each clone instance has y nodes, we perform:

%\begin{equation}\label{eq:sameclass}
%\frac{x * (x + 1)}{2} * y
%\end{equation}

%comparisons to determine the relation. Each of these checks will result in one of the relations from the list above. Of these relations, the item lowest in the list is going to be the relation of the clone class. So for instance, if a clone class has 15 nodes that denote a \textit{Superclass} relation but 3 nodes are \textit{Unrelated}, the clone class becomes \textit{Unrelated}.

@@

 %We define the method as the first method declaration that is encountered when following the parent nodes in the AST for a given cloned node. %Please note that a clone instance may not always be in a method, for which this predicate will fail.

%Clone classes are flagged as \textit{Same method} if all their clone instances are found in the same method. Cloned classes are flagged as \textit{Same class} if all their clone instances are found in the same class. %We define the class as the first class declaration that is encountered when following the parent nodes in the AST for a given cloned node.

\subsubsection{Common Hierarchy}
Clones that are in a common hierarchy can be refactored by using the ``Extract Method'' refactoring method followed by ``Pull Up Method'' until the method reaches a location that is accessible by all clone instances. However, the more often ``Pull Up Method'' has to be used, the more detrimental the effect is on system design. This is because putting a lot of functionality in classes higher up in an inheritance structure can result in the ``God Object'' anti-pattern. A god object is an object that knows too much or does too much \cite{fowler2018refactoring}.

%Clone classes are flagged as \textit{Superclass} if the classes in which the clone instances are found are parent and child class of each other. Clone classes are flagged as \textit{Siblings} if the classes in which their clone instances are found all share the same parent and this parent class is not external. Clone classes are flagged as \textit{First Cousin} if the classes in which their clone instances are found all share the same grandparent and this grandparent class is not external.

%Clone classes nodes are flagged as \textit{Ancestor} if the classes in which their clone instances are found are recursively the parent of an antecedent. Cloned nodes are flagged as \textit{Same Hierarchy} if the classes in which these nodes are found are all in the same inheritance hierarchy and not linked by any external classes.

@@

%To check whether two cloned nodes have a \textit{Same Direct Interface} relation, we check that the classes to which these nodes belong both implement the same interface type. To check whether two cloned nodes have a \textit{Same Indirect Interface} relation, we recursively walk all types the class or interface of the cloned nodes implement and extend. The common interface that is closest to the cloned node in terms of depth of recursion will be flagged as the refactoring candidate.

@@

Cloned classes with a \textit{No Direct Superclass} relation mark the opportunity for creating a superclass abstraction and placing the extracted method there. For clone classes with a \textit{No Indirect Superclass} relation, CloneRefactor creates such an abstraction for the ancestor that does not have a parent. Clone classes with a \textit{External Superclass} or \textit{External Ancestor} relation obstruct the possibility of creating a superclass abstraction. In such a case, CloneRefactor creates an interface abstraction to make their relation explicit.

%Cloned nodes are flagged \textit{No Direct Superclass} if they are in classes that do currently not have a parent. This marks the opportunity for creating a superclass abstraction and placing the extracted method there. Cloned nodes are flagged \textit{No Indirect Superclass} if any of their ancestors do not have a parent. In such a case, it would be possible to create such an abstraction for the ancestor that does not have a parent.

%Cloned nodes are flagged \textit{External Superclass} if they are in a class which has an external parent. Cloned nodes are flagged \textit{External Ancestor} if one of their ancestors has an external parent. Both of these relations obstruct the possibility of creating a superclass abstraction. In such a case, an interface abstraction could be created to make their relation explicit.
